\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-09-17 manuscript/cov.tex
switch sentence order

Our paper addresses a gap in the application of the Kolmogorov-Smirnov
(KS) test for assessing the marginal goodness-of-fit of hypothesized
distributions in the context of serially dependent stationary
observations. While parametric block bootstrap procedures typically
require specification of the serial dependence structure, a
nonparametric block bootstrap procedure is advantageous as it avoids
this requirement. The nonparametric block bootstrap version of the KS
test extends the nonparametric approach studied by Basu and Rao
(2004) to cases of serial dependence. However, such a version does not
yet exist, and our paper fills this gap. The proposed test has wide
applications in time series modeling, particularly in scenarios where
marginal distributions are of interest, such as in financial time series.

>>>>

Our paper addresses a gap in the application of the Kolmogorov-Smirnov
(KS) test for assessing the marginal goodness-of-fit of hypothesized
distributions in the context of serially dependent stationary
observations. While parametric block bootstrap procedures typically
require specification of the serial dependence structure, a
nonparametric block bootstrap procedure is advantageous as it avoids
this requirement. However, such a nonparametric block bootstrap procedure does 
not yet exist, and our paper fills this gap. The proposed nonparametric block 
bootstrap version of the KS test extends the nonparametric approach studied by 
Basu and Rao (2004) to cases of serial dependence.  The proposed test has wide
applications in time series modeling, particularly in scenarios where
marginal distributions are of interest, such as in financial time series.
